### 2014-05-01 paper.tex
Reverted changes that should never have changed...

We will begin by describing some of the background, the motivation and the details in the Robotics Challenge, focusing on the properties and the limitations of the hardware.  The next section considers the software and the

@@

\subsection{DBI Behaviors}
Boston Dynamics provided predefined behaviour for Atlas, each of these controllers can be activated from state to another state.

@@

Although it could be automated, it is also usually required for the driver to additionally modify the final two steps such that they are further apart, thus providing a stronger base for the walking.

@@

The initial approach to complete this task was to use the Boston Dynamics motion controller, and perform the motion by solving for different positions using the MoveIt!, but it quickly presented several problems, such as when solving for the 6-dof arm, it would only sometimes find a solution and unable to complete the full motion, and when using 6-dof arm + 3-dof back joints, it would use the back way too much for the motions and cause unpredictable behaviour.

The final approach was Carnigue Mellon's controller, and allowing a human operator to choose in which quadrantal direction to move the end effector, and analyse the force being applied to the hand, and move the hand in which ever direction necessary.

@@

\section{DRC Wall}
\begin{wrapfigure}{r}{0.3\textwidth}
  \begin{center}
    \includegraphics[scale=0.5]{images/drilling2.png}
  \end{center}
  \caption{The front camera vision of drilling the wall}
\end{wrapfigure}
For the Wall task the robot must use a single handed cordless rotary tool with an on/off switch to cut and remove a prescribed triangular shaped piece from a wall. The wall material will be 0.5 inch thick drywall. The three vertices of the right triangle will be 6 inches diameter circles. The edges connecting the vertices will be 6 inches wide. The vertical edge will be 12 inches long, and the horizontal edge will be 24 inches long. The bottom of the triangle will be 36 inches above the ground. \cite{walltask}
\subsection{Approach}
\subsection{Results}
\subsection{Conclusion and Future Work}

>>>>

We will begin by describing some of the background, the motivation and the details in the Robotics Challenge, focusing on the properties and the limitations of the hardware.  The next section considers the software, starting at the overall infrastructure, and going into more detail about the manipulation software.

@@

\subsection{DBI Behaviors}
Boston Dynamics provided predefined behaviours for Atlas that allow for basic performance like balancing and walking. Transitions between behaviors can occur manually or automatically, and follow a pre-determined state-machine.

@@

Although it could be automated, it is also usually required for the operator to additionally modify the final two steps such that they are further apart, thus providing a larger support polygon for manipulation.

@@

The initial approach to complete this task was to use the Boston Dynamics motion controller, and perform the motion by solving for different positions using MoveIt!, but this approach quickly presented several problems, such as when solving for the 6-dof arm, it would only occasionally find a solution, and it was unable to complete the full motion. Another problem arised when using the 6-dof arm + 3-dof back joints, MoveIt! would use the back joints way too much for the motions and cause unpredictable behaviour.

The final method used the Carnigue Mellon's Full-body controller. This allowed a human operator to choose in which quadrantal direction to move the end-effector, analyze the force being applied to the hand, and move the hand in which ever direction necessary.

@@

\section{DRC Wall}
\begin{wrapfigure}{r}{0.3\textwidth}
  \begin{center}
    \includegraphics[scale=0.5]{images/drilling2.png}
  \end{center}
  \caption{The front camera vision of drilling the wall}
\end{wrapfigure}
For the Wall task the robot must use a single handed cordless rotary tool with an on/off switch to cut and remove a prescribed triangular shaped piece from a wall. The wall material will be 0.5 inch thick drywall. The three vertices of the right triangle will be 6 inches diameter circles. The edges connecting the vertices will be 6 inches wide. The vertical edge will be 12 inches long, and the horizontal edge will be 24 inches long. The bottom of the triangle will be 36 inches above the ground. \cite{walltask}

\subsection{Approach}
Performing the Wall task was a bit of a challenge for two reason: \begin{inparaenum}[\itshape a\upshape)]
\item Being able to progress the power-tool trigger and 
\item having the mobility to cut the wall in one motion. \end{inparaenum}

\subsubsection{Picking up the drill}
Finding the drill on the point cloud is mostly a trivial task for the robot operator. Specially since the hight of the table was given in the task description. On the robot walked to the table, DARPA gave the option to choose one of two drills:

\begin{itemize}
\item One Dewalt DCD980M2 cordless drill: The robot must grasp the drill and squeeze the trigger to maintain the drill on. The drill also has a side handle to help with maneuverability. The problem with this drill is that the Robotiq hand had no way to firmly grasp the handle and press the trigger at the same time. The shape of the handle would cause the hand's middle finger on the back side of the drill to push out the front finger out of the trigger whenever any kind of firm grasp was applied.

\item Dewalt DC550 cordless drill: It has an on/off switch. It was quite easy to grasp and operate, but pressing the small button on the base of the drill was quite difficult with the robot's large hands. The most reliable solution that we found is to shake the drill after grasping it, and add an extension on the hand such that it presses on the ON button.  Since the battery asymmetrical, the heavier side always slowly moves towards the ground, and causes the ON button to fall onto the hand's added extrusion. 
\end{itemize}

We found that the DC550 was the best option. The drill also provided a much wider range of motion while moving the arms.

\subsubsection{Cutting the wall}
Once the drill was turned on, the robot would walk towards the wall and position his right shoulder parallel to the bigger side of the triangle. Once the robot start cutting the wall, the two main issues were:  \begin{inparaenum}[\itshape a\upshape)]
\item Ensuring that the drill bit was far enough in the wall, and  
\item The battery of the drill was not drained. \end{inparaenum}

DARPA promised the teams that the drill would be fully charged at the beginning of each run, but during one practice run before the competition, the battery ran out before finishing the first cut. The controller quite reliability able to perform the entire motion without having to take a step. The operator would tell the robot to move one centimeter at a time in a direction, and monitor the hand forces applied.

\subsection{Results}
During the competition, the operator made an error in the robot operation mode. Each of the hands has the option to either move the hand by setting a position relative to the floor, setting fixed joint values. While the right hand, which is operating the drill, is used with relative positions, the left hand is left at fixed joint values, not to add additional constraints to the kinematics.

The left hand was accidentally turned on into relative positions, and since there were no graphical feedback about the operation of each hand, the operator was unable to determine why the robot was unable to move as freely as necessary to cut the wall. On an attempt to reset the controller while the robot was still running to fix the unexpected behavior, the robot fell, having to reset the task.

On the second attempt, the team only had about 10 minutes left to perform the task, and while it was possible to grab and turn on the drill, the robot was unable to finish the first cut in time.

\subsection{Conclusion and Future Work}

The approach of the task was solid and presented little issues most of the times. Due to the operator stress, and lack of visual cues about the robot state, the task was not completed. It is also feasible to perform the task autonomously with the current technology and resources.
